Simulation Study of Angular Resolution of a New Electromagnetic Sampling Calorimeter

### 2022-06-11 paper.tex
updates

Figure~\ref{fig:res_edep} shows estimated $p_{1}$ as a function of the incidence angle. $p_{0}$ and $p_{1}$ are consistent for $\theta>$~10$^{\circ}$ and estimated to be 0.29$^{\circ}$ and 1.24$^{\circ}$, respectively. For small $\theta$, $p_{1}$ is smaller than larger $\theta$ as the angular resolution is significantly dependent on the incidence angle for the low incident energy.

@@

Figure~\ref{fig:multi-parameter} shows the angular resolution with different numbers of training samples for different detector configurations. All configurations show a decrease in the angular resolution with increasing training samples, which means that enhanced statistics for the training results in better reconstruction. The angular resolution with 5-mm-wide scintillator strips decreases more rapidly than others. The number of features for the 5-mm-wide strip is much larger than others, and the number of training samples is much required to correlate larger features. Considering limited computing resources, the setup with $10^{5}$ events, 24 layers, and the 15-mm-wide strip was chosen for training the XGB model. The training result differs by only 0.2$^{\circ}$ from the best setup will full layers.

>>>>

Figure~\ref{fig:res_edep} shows estimated $p_{1}$ as a function of the incidence angle. $p_{0}$ and $p_{1}$ are consistent for $\theta>$~10$^{\circ}$ and estimated to be 0.29$^{\circ}$ and 1.24$^{\circ}$, respectively. For small $\theta$, $p_{1}$ is smaller than larger $\theta$ from the fact that the angular resolution is largely dependent on the incidence angle for the low incident energy.

@@

Figure~\ref{fig:multi-parameter} shows the angular resolution with different numbers of training samples for different detector configurations. All configurations show a decrease in the angular resolution with increasing training samples, which means that enhanced statistics for the training results in better reconstruction. The angular resolution with 5-mm-wide scintillator strips decreases more rapidly than others. The number of features for the 5-mm-wide strip is much larger than others, and the number of training samples is much required to correlate larger features. Considering limited computing resources, the setup with $10^{5}$ events, 32 layers, and the 15-mm-wide strip was chosen for training the XGB model. The training result differs by only 0.$^{\circ}$ from the best setup will full layers.
